Modal Abstractions for Virtualizing Memory Addresses

### 2023-04-12 examples.tex
+
done with Section 6.2

$\specline{\textsf{P} \ast \mathcal{I}\texttt{ASpace} (<[\vaddr:=\texttt{fpaddr}]> \theta,\gammaPred) \ast  \texttt{r14}\mapsto_{r} \texttt{pte\_addr} \ast \texttt{rdi}\mapsto_{r} \vaddr \; \ast}_{\rtv}$

@@

Finally, we can insert $\vaddr$ into the ghost page-table-walk summarization map ($\theta$) to change its state from unmapped ($\ulcorner \theta \;!!\;\vaddr = \texttt{None}\urcorner$ in Specification Line 30) to mapped, and construct virtual-pointsto for $\sumwalkabs\vaddr\qfrac\fpaddr$ with fragmental ownership of

After storing $\textsf{pte\_addr}$
%\todo[inline]{emphasize the write to the L1 page table is validated by the fact that the identity mapping exists}
\subsection{Unmapping a Page}
The reverse operation, unmapping a designated page that is currently mapped, is pleasingly the reverse: by flipping the entry back to an invalid entry, full ownership of the updated entry reverts back to the now-invalid cell of the L1 table.

>>>>

$\specline{\textsf{P} \ast \mathcal{I}\texttt{ASpace} (<[\vaddr:=\texttt{fpaddr}]> \theta,\gammaPred) \ast}_{\rtv}$

@@

Finally, we can insert $\vaddr$ into the ghost page-table-walk summarization map ($\theta$) to change its state from unmapped ($\ulcorner \theta \;!!\;\vaddr = \texttt{None}\urcorner$ in Specification Line 30) to mapped (Specification Line 33), and construct virtual-pointsto $\vaddr \mapsto_{\textsf{vpte}}\; \qfrac \;\fpaddr \textsf{ wzero 64}$ (Specification Line 36) with $\sumwalkabs\vaddr\qfrac\fpaddr$ obtained from ghost page-table-walk insertions, $\sumapaces\rtv\delta$ from unfolding the definition of $\mapsto_{\textsf{vpte}}$ in Specification Line 18, and $\fpaddr \mapsto_{\textsf{p}} \textsf{wzero 64}$ in Specification Line 34. fragmental ownership of 
\subsection{Unmapping a Page}
The reverse operation, unmapping a designated page that is currently mapped, is pleasingly the reverse: by flipping the entry back to an invalid entry, full ownership of the updated entry reverts back to the now-invalid cell of the L1 table.
